---
title: "Analysis"
subtitle: "Workflow"
author: "Daniel Cusimano"
date: "08/15/2024"
output: html_document
---

# Data Analysis in R Workflow


## Purpose and Design

This page needs to be broken into two: one for processing and the other for analysis. The processing page will work through how the data from 3D Slicer is imported and modified into the needed file types for Geometric Morphometric analysis. The following page will then consolidate the needed analytical results and graphics for a simplified review. 

This markdown file utilizes codechunks.
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('SLanalysis.r')
```

Load needed packages

```{r, Loadpackages, message=FALSE, warning=FALSE}
library(rgl)
setupKnitr(autoprint = TRUE)
```

## Importing Data

The process for imported Slicer Data into a workable format in R was followed from the SlicerMorph/Tutorials page at `https://github.com/SlicerMorph/Tutorials/blob/main/GPA_3/parser_and_sample_R_analysis.md`. The instructions provided by this page were followed closely and adjusted if/when they did not provide the needed results. 

The primary file needed from the slicer export is the analysis.log file. This contains all of the objects generated by SlicerMorph's GPA Module. These objects are parsed by `parser()` and stored in the SM.log list as individual objects. The SlicerMorph Tutorial suggests using `parser2()` for this process but this did not work for my files. 

```{r, loaddata}
```

Merge Demographic data with Landmark data

```{r, merge}
```

Build array from Slicer data

```{r, BuildingArray}
```

```{r, Array}
```

Run preliminary analyses

```{r, GPA}
```

```{r, fourplot}
```

```{r, gdf}
```

```{r, Plotpoints}
```