---
title: "Analysis"
subtitle: "Workflow"
author: "Daniel Cusimano"
date: "08/15/2024"
output: html_document
---

# Data Analysis in R Workflow


## Purpose and Design

This page is still in progress. From the data obtained via SlicerMorph and the step described on the [`processing`](data_processing.qmd) page, I am running ANOVA and PCA analyses. Running the statistics and understanding the superficial insights is pretty straightforward. Some of the more detailed analysis, however, still need to be worked out. 

This markdown file utilizes codechunks.
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('SLanalysis.r')
```

Load needed packages

```{r, Loadpackages, message=FALSE, warning=FALSE}
library(rgl)
setupKnitr(autoprint = TRUE)
```

## Importing Data

The primary file needed from the slicer export is the analysis.log file. This contains all of the objects generated by SlicerMorph's GPA Module. These objects are parsed by `parser()` and stored in the SM.log list as individual objects. The SlicerMorph Tutorial suggests using `parser2()` for this process but this did not work for my files. 

```{r, loaddata}
```


# GPA

This will be the start of this page. 

```{r, GPA}
```

```{r, fourplot}
```

```{r, gdf}
```
