---
title: "Analysis"
subtitle: "Workflow"
author: "Daniel Cusimano"
date: "08/15/2024"
output: html_document
---

# Data Analysis in R Workflow


## Purpose and Design

This page is still in progress. From the data obtained via SlicerMorph and the step described on the [`processing`](data_processing.qmd) page, I am running ANOVA and PCA analyses. Running the statistics and understanding the superficial insights is pretty straightforward. Some of the more detailed analysis, however, still need to be worked out. 

This markdown file utilizes codechunks.
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('SLanalysis.r')
```

Load needed packages

```{r, Loadpackages, message=FALSE, warning=FALSE}
library(rgl)
setupKnitr(autoprint = TRUE)
```

## Importing Data

The files used in this analysis were produced in the processing code (`SLprocess.r`) illustrated in the `Data Processing` page on this website. The files listed below represent only the material thus far used. More data may be added as this project continues. 

```{r, loaddata}
```


# PCA

The primary statistical approach first applied is a Principal Components Analysis. The next three plots below illustrate the initial results of PC1 by PC2, followed by color coded modifiers to visualize how the plotted variation relates to the sample demographics. 

```{r, PCA}
```

The collage below shows the original PC1 by PC2 compared with analyses by three different planes. Unsurprisingly, the original analysis shows the most variation and the strongest clustering by ancestry. This collage also labels the PC axes for me which I haven't figured out how do yet for the larger plots. Everything is still a work in progress. 

```{r, fourplot}
```

```{r, gdf}
```
