---
title: "Analysis"
subtitle: "Workflow"
author: "Daniel Cusimano"
date: "08/15/2024"
output: html_document
---

# Data Analysis in R Workflow


## Purpose and Design

This page is still in progress. From the data obtained via SlicerMorph and the step described on the [`processing`](data_processing.qmd) page, I am running ANOVA and PCA analyses. Running the statistics and understanding the superficial insights is pretty straightforward. Some of the more detailed analysis, however, still need to be worked out. 

This markdown file utilizes codechunks.
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('SLanalysis.r')
```

Load needed packages

```{r, Loadpackages, message=FALSE, warning=FALSE}
library(rgl)
setupKnitr(autoprint = TRUE)
```

## Importing Data

### Redundant Info until updated. Jumpt to GPA

The process for imported Slicer Data into a workable format in R was followed from the SlicerMorph/Tutorials page at `https://github.com/SlicerMorph/Tutorials/blob/main/GPA_3/parser_and_sample_R_analysis.md`. The instructions provided by this page were followed closely and adjusted if/when they did not provide the needed results. 

The primary file needed from the slicer export is the analysis.log file. This contains all of the objects generated by SlicerMorph's GPA Module. These objects are parsed by `parser()` and stored in the SM.log list as individual objects. The SlicerMorph Tutorial suggests using `parser2()` for this process but this did not work for my files. 

```{r, loaddata}
```

Merge Demographic data with Landmark data

```{r, merge}
```

Build array from Slicer data

```{r, BuildingArray}
```

```{r, Array}
```

# GPA

This will be the start of this page. 

```{r, GPA}
```

```{r, fourplot}
```

```{r, gdf}
```

```{r, Plotpoints}
```